---
title: "linear model from Web"
author: "Jaylen Johnson"
date: "Spring 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size=22))
```
  
This data shows a simulation of the expectaions of the arm strength in the workers. This tells us that it is epxected for most of the population to have between 50 and 100 arm strength. 





### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

  
The larger this number is, the larger the correlation between the two factors is.  From this data, it shows that there is a small correlation between the factors since the number is near 1. 



### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

  
The equation for the line of this scenario is SIMS=0.054563 x ARM -4.095160.  Since the coeffecient is positive the line increases moving from the lower left corner to the upper right corner.  


#### Predict at target point

```{r}
tgtpoint=data.frame(ARM=88, GRIP=94)
predict(model.1, tgtpoint, interval = c("prediction"))
```
  
The information presented here shows the predicted target plot is 0.7063836 95% of the time and that the value can range from -1.726209 to 3.138977.

#### scatterplot with model fit
  
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size=22)) + geom_smooth(method=lm)
```
This plot shows the line of best fit from data points collected from SIms vs Arms, showing what data poinys are closest to the expected results.


## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
basicGRIP <- ggplot(data,aes(y=SIMS,x=GRIP))
```
```{r}
basicGRIP + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size=22))
```



### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

